Binary companions of red giant stars with APOGEE DR14

### 2018-02-23 paper/1-catalog/twoface-catalog.tex
moved some figures around text

\todo{Explain that this is the procedure, but two full runs described below in results...}

>>>>

Here we describe the procedure we use to generate per-target posterior samplings
for the \apogee\ targets.
We execute the full procedure twice for different goals (as described in
\sectionname~\ref{sec:results}), and only here outline the key steps in the
pipeline.
